### 2025-01-16 paper/experiments/README.qmd
updated job scripts
vamos
try lin_sep first
minor things

>>>>

## Command Line Usage

```
sbatch --ntasks=$(determine_resources) --cpus-per-task=$NTHREADS myfile.sh
```

```
sbatch --ntasks=$(determine_resources --data=mydata --model=mymodel) --cpus-per-task=$NTHREADS myfile.sh --data=mydata --model=mymodel
```

:::{.callout-warning}
The extra arguments `--data=mydata --model=mymodel` should be consistent, i.e. they should be passed consitently to `determine_resources` and the whole `sbatch` command. 
:::

## Interactive Usage
